### 2009-07-01 docs/runtime_parameters/runtime_parameters.tex
updated with script

\verb=  interp_type_radial_bin_to_cart  = &   The interpolation for filling a full multifab from a 1D bin-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear.  &  1 \\

@@

\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  -1 \\

@@

\verb=  p0_update_type  = &   How we update the base state pressure and compute psi. \newline 1 = call {\tt advect\_base\_pres}; \newline 2 = call {\tt enforce\_HSE}.  &  1 \\

@@

@@

\verb=  w0mac_interp_type  = &   0 = Compute w0 at edges using a projection; \newline 1 = Interpolate w0 to cell centers, then average to edges; \newline 2 = Interpolate w0 to edges directly;                \newline 3 = Interpolate w0 to nodes, then average to edges.  &  1 \\

>>>>

@@

\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\

@@

\verb=  p0_update_type  = &   How we update the base state pressure and compute psi. \newline 1 = call {\tt advect\_base\_pres}; \newline 2 = call {\tt enforce\_HSE}.  &  2 \\

@@

\verb=  s0_interp_type  = &   The interpolation for filling a cell-centered multifab from a 1D bin-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear.  &  1 \\
\verb=  s0mac_interp_type  = &   The interpolation for filling an edge based multifab from a 1D bin-centered array. \newline 1 = Interpolate s0 to cell centers, then average to edges; \newline 2 = Interpolate s0 to edges directly;                \newline 3 = Interpolate s0 to nodes, then average to edges.  &  1 \\

@@

\verb=  w0mac_interp_type  = &   The interpolation for putting w0 on edges.  We only compute the normal component. \newline 1 = Interpolate w0 to cell centers, then average to edges; \newline 2 = Interpolate w0 to edges directly;                \newline 3 = Interpolate w0 to nodes, then average to edges.  &  1 \\
